---
title: "PQ Report Generator"
version: "v1.4.1"
author: "Kyle"
date: "`r Sys.Date()`"
output: 
     html_document:
          toc: true
params:
     directory: "C:/Users/ks0316/Documents/PQReportCompiler"
     assay: "paraflu"
     worklist.id: "C:/Users/ks0316/Documents/PQReportCompiler/worklist.id.csv"
     limits: "C:/Users/ks0316/Documents/PQReportCompiler/assay.limits.csv"
     lof: "nonspecified"
     analysis.id: "generic analysis.html"
     graphing: "FVF"

---
<style>
body {
    position: absolute;
    left: 10px;}

table {
    text-align: left;
    border-collapse: collapse;
    width: 100%;
}

th, td {
    text-align: left;
    padding: 8px;
}

tr:nth-child(even){background-color: #f2f2f2}

th {
    text-align: left;
    background-color: #00008B;
    color: white;
}

</style>

#Parameters Entered
```{r set-options, echo=FALSE, cache=FALSE}
### test cases
# params:
#      directory: "T:/Public/Kyle S/PCR"
#      assay: "paraflu"
#      worklist.id: "C:/Users/ks0316/Documents/PQReportCompiler/worklist.id.csv"
#      limits: "T:/CoreTeams/Radium/Assay Development_Orig/Kyle S/PQ Data/assay.limits.csv"
#      lof: "nonspecified"

# params = data.frame(directory="T:/Public/Kyle S/PCR",
#                     assay = "paraflu",
#                     worklist.id="T:/CoreTeams/Radium/Assay Development_Orig/Kyle S/PQ Data/worklist.id.csv",
#                     limits="T:/CoreTeams/Radium/Assay Development_Orig/Kyle S/PQ Data/assay.limits.csv",
#                     stringsAsFactors = FALSE)

### At home testing
# params = list(directory="C:/Users/ks0316/Documents/PQReportCompiler",
#                     assay = "paraflu",
#                     worklist.id="C:/Users/ks0316/Documents/PQReportCompiler/worklist.id.csv",
#                     limits="C:/Users/ks0316/Documents/PQReportCompiler/assay.limits.csv",
#                     lof="nonspecified",
#                     analysis.id="generic title.html",
#                     graphing="FVF"
#                     # graphing="time"
# )

# if(params$lof == "nonspecified"){
#      cat(params$directory)
# } else if(params$directory == "nonspecified"){
#      cat(params$lof)
# }

print(params)
```

```{r, warning=FALSE, message=FALSE, include=FALSE, cache=FALSE}
library(dplyr)
library(ggplot2)
library(tidyr)
library(lubridate)
library(stringr)
library(formattable)
library(DT)
library(htmltools)
library(knitr)
# setwd("T:/CoreTeams/Radium/Assay Development_Orig/Kyle S/PQ Data")
# setwd("C:/Users/ks0316/Documents/PQReportCompiler")
source(file="./allFunctions2.R")
wlid = read.csv(params$worklist.id, stringsAsFactors = FALSE)
if(params$limits != "nonspecified"){
     assay.limits = read.csv(params$limits, stringsAsFactors = FALSE)
}

if(params$lof == "nonspecified"){
     setwd(params$directory)
     lof = list.files(pattern="@DI", path=params$directory, full.names = T)

     a = basename(lof)
     b=strsplit(a, split="_")
     c=lapply(b, `[[`, 1)
     d = unlist(c)
     filt.v=!grepl(pattern="@DI", d)
     lof = lof[filt.v] #filtered list of files
     rm(a, b, c, d, filt.v)
} else{
     lof = params$lof
}
### test case
# lof = c("C:/Users/ks0316/Documents/_Mucin PQs/20160714-1330/@DI2090001330-20160715-001920-001330-20160714-05-07.csv",
# "C:/Users/ks0316/Documents/PQReportCompiler/@DI209000001-20160526-044112-001099-20160525-10.csv",
# "C:/Users/ks0316/Documents/PQReportCompiler/@DI209000001-20160603-164000-000001-20160602-06.csv",
# # "T:/Public/Kyle S/PCR/@DI209000001-20160622-161243-000001-20160621-05.csv",
# "C:/Users/ks0316/Documents/PQReportCompiler/@DI209000001-20160613-161934-000001-20160602-06.csv",
# "C:/Users/ks0316/Documents/PQReportCompiler/@DI209000001-20160622-161243-000001-20160621-05.csv")
# "T:/CoreTeams/Radium/Assay Development_Orig/Kyle S/PQ Data/_Assay/2016_06_02 F51 PQ/@DI209000001-20160603-164000-000001-20160602-06.csv")
pq0 = appender(lof, grabber)

if(all(pq0$list.output$loaded == "LOADED")){
     pq0 = pq0$pq.data
     cat("All files have been loaded.")
} else{
     pq0 = pq0$pq.data
     cat("Some files had issues being loaded, see output.")
     print(pq0$list.output$files[pq0$list.output$loaded != "LOADED"])
}

#Round down RFU Range
pq0$RFU.Range = floor(pq0$RFU.Range)
pq0$ct = signif(pq0$ct, digits=4)

### Special Escape characters
pq0$Sample.Name = gsub("`", "battick", pq0$Sample.Name)
pq0$Sample.Name = gsub("\\\\", "double-slash", pq0$Sample.Name)

# pq = categorizer(pq, params$assay)
pq0 = categorizer(pq0, inputfile = wlid)

# pq0 %>% select(Sample.Name, sample.type) %>% utils::View()

uncat = pq0 %>%
     group_by(filename) %>%
     summarise(Uncategorized = sum(is.na(sample.type)))

### Will implement code in next version with Shiny
# setwd(dirname(params$file))
# temp.file = list.files(pattern="TCYC.csv$", recursive = TRUE, full.names = TRUE)
# tcyc_raw = tcyc_reader(temp.file, pq0)

if(!exists(x="assay.limits")){
     assay.limits = structure(list(sample.type = c("Positive Control", "Positive Control", 
     "Positive Control", "Positive Control", "Positive Control", "Panel C", 
     "Panel C", "Panel C", "Panel C", "Panel C", "Panel A", "Panel A", 
     "Panel A", "Panel A", "Panel A", "Negative Control", "Negative Control", 
     "Negative Control", "Negative Control", "Negative Control"), 
         Channel = c("FAM", "HEX", "IC", "RED647", "ROX", "FAM", "HEX", 
         "IC", "RED647", "ROX", "FAM", "HEX", "IC", "RED647", "ROX", 
         "FAM", "HEX", "IC", "RED647", "ROX"), threshold = c(1200L, 
         2000L, 500L, 400L, 1500L, 1200L, 2000L, 500L, 400L, 1500L, 
         500L, 500L, 2000L, 350L, 500L, 500L, 500L, 2000L, 350L, 500L
         ), direction = c("min", "min", "min", "min", "min", "min", 
         "min", "min", "min", "min", "max", "max", "min", "max", "max", 
         "max", "max", "min", "max", "max")), .Names = c("sample.type", 
     "Channel", "threshold", "direction"), class = "data.frame", row.names = c(NA, 
     -20L))     
}

## Filtering logical vectors
pslv = quote(sample.type == "Panel C" | sample.type == "Positive Control")
nslv = quote(sample.type == "Panel A" | sample.type == "Negative Control")

## Data type manipulation
# pq0$sample.type = as.factor(sort(as.character(pq0$sample.type)))
# pq0$Channel = as.factor(sort(as.character(pq0$Channel)))
# assay.limits$sample.type = as.factor(sort(as.character(assay.limits$sample.type)))
# assay.limits$Channel = as.factor(sort(as.character(assay.limits$Channel)))

pq0[,c("sample.type", "Channel")] = lapply(pq0[,c("sample.type", "Channel")], as.character)
assay.limits[,c("sample.type", "Channel")] = lapply(assay.limits[,c("sample.type", "Channel")], as.character)

pq = left_join(pq0, assay.limits, by=c("sample.type", "Channel"))

pq = pq %>%
     mutate(pass = ifelse((direction=="min" & RFU.Range > threshold) | (direction=="max" & RFU.Range < threshold), "PASS", "FAIL")) %>%
     mutate(hits=ifelse(pass == "PASS", 1, 0))
```

# PQ Result
``` {R, result='asis', echo=FALSE, cache=FALSE, warning=FALSE, message=FALSE}
summary.pq = pq %>%
     group_by(filename, FusionAssayVersion, pantherSN, Channel, sample.type) %>%
     summarise(Mean.RFU.Range = mean(RFU.Range, na.rm=T), Max.RFU.Range = max(RFU.Range, na.rm=T), Min.RFU.Range=min(RFU.Range, na.rm=T),
               N = n(), Positive = sum(hits),
               Mean.Ct = mean(ct, na.rm=T), Sd.Ct = sd(ct, na.rm=T),
               Max.Ct = max(ct, na.rm=T), Min.Ct = min(ct, na.rm=T)) %>%
     mutate(CV = Sd.Ct/Mean.Ct*100, Pass.Fail = ifelse(N == Positive, 1, ifelse(Channel == "RED647" & N-Positive <= 2, 1, 0)))

summary1.pq = pq %>%
     group_by(Software.Revision, Channel, sample.type) %>%
     summarise(Mean.RFU.Range = mean(RFU.Range, na.rm=T), Max.RFU.Range = max(RFU.Range, na.rm=T), Min.RFU.Range=min(RFU.Range, na.rm=T),
               N = n(), Positive = sum(hits),
               Mean.Ct = mean(ct, na.rm=T), Sd.Ct = sd(ct, na.rm=T),
               Max.Ct = max(ct, na.rm=T), Min.Ct = min(ct, na.rm=T)) %>%
     mutate(CV = Sd.Ct/Mean.Ct*100, Pass.Fail = ifelse(N == Positive, "PASS", ifelse(Channel == "RED647" & N-Positive <= 2, "PASS", "FAIL")), Hits = paste(Positive, N, sep="/")) %>%
     ungroup() %>% select(Channel, sample.type, Mean.RFU.Range, Max.RFU.Range, Min.RFU.Range, Mean.Ct, Sd.Ct, Max.Ct, Min.Ct, CV, Hits) %>%
     arrange(sample.type)

summary1.pq$CV = percent(summary1.pq$CV)/100
summary1.pq$Mean.RFU.Range = floor(summary1.pq$Mean.RFU.Range)
summary1.pq[,c("Mean.Ct", "Sd.Ct")] = lapply(summary1.pq[,c("Mean.Ct", "Sd.Ct")], signif, digits=4)

condensed.summary =
     summary.pq %>%
     ungroup() %>%
     group_by(filename, FusionAssayVersion, pantherSN) %>%
     summarise(PQ.PF=sum(Pass.Fail), count = n()) %>%
     mutate(Chemistry.Pass =ifelse(PQ.PF == count, 1, 0))

# flaggregator(df = pq, assay=params$assay) %>% utils::View()

c.summary2 = left_join(condensed.summary, flaggregator(df = pq, assay=params$assay), by="filename")
c.summary2 = other_flags(c.summary2)

if(params$assay=="paraflu"){
     c.summary3 = c.summary2 %>%
          group_by(filename, FusionAssayVersion, pantherSN, Flags) %>%
          summarise(Result = ifelse(Chemistry.Pass == 1 & VVFS <= 6 & other.flags == TRUE, "PASS",
                                    ifelse(other.flags == FALSE, "PENDING", "FAIL")))
} else{
     c.summary3 = c.summary2 %>%
          group_by(filename, FusionAssayVersion, pantherSN, Flags) %>%
          summarise(Result = "PENDING")
}

c.summary3$Uncategorized.Samples = uncat$Uncategorized

datatable(c.summary3, list(Result = formatter("span",
style = x ~ ifelse(x == "PASS", style(color="green"),
ifelse(x =="PENDING", style(color="orange"), style(color="red"))))))
```

# Summary statistics of PQ
``` {R, result='asis', echo=FALSE, cache=FALSE}
s1.pq.t = summary1.pq %>%
     filter(grepl("Panel", sample.type)) %>%
     select(sample.type, Channel, everything()) %>%
     rename(Sample.Type=sample.type) %>%
     t()
s1.pq.t[is.na(s1.pq.t)] = "-"
formattable(as.data.frame(s1.pq.t))
# summary1.pq$filename = as.factor(summary1.pq$filename)

s2.pq.t = summary1.pq %>%
     filter(grepl("Control", sample.type)) %>%
     select(sample.type, Channel, everything()) %>%
     rename(Sample.Type=sample.type) %>%
     t()
s2.pq.t[is.na(s2.pq.t)] = "-"
formattable(as.data.frame(s2.pq.t))
# summary1.pq$filename = as.factor(summary1.pq$filename)
# temp = split(summary1.pq, summary1.pq$filename, drop=TRUE)
# 
# show_plot <- function(plot_object){
#   div(style="margin:auto;text-align:center", plot_object)
# }
```

# Pass / Fail Criteria
##Assay Defined Thresholds
``` {R, result='asis', echo=FALSE}
assay.limits.t = assay.limits %>%
     filter(grepl("Panel", sample.type)) %>%
     mutate(Threshold=ifelse(direction=="min", paste0(">", threshold), paste0("<", threshold))) %>%
     rename(Sample.Type=sample.type) %>%
     select(Sample.Type, Channel, Threshold) %>%
     t()
     
formattable(as.data.frame(assay.limits.t))
```

# Positive Samples
Raw RFU.Range data of Panel C and Positive Control (if present):
``` {R, result='asis', echo=FALSE, cache=FALSE}
long.to.wide = function(df=pq){
     df=pq
     spreaded = df %>%
          select(-pass, -threshold, -direction) %>%
          unite(col=metrics, ct, tslope, RFU.Range, EstimatedBaseline, hits) %>%#utils::View()
          spread(Channel, metrics)
     spreaded2 = spreaded %>%
          separate(col="FAM", into=c("FAM.ct", "FAM.tslope", "FAM.rr", "FAM.eb", "FAM.result"), sep="_") %>%
          separate(col="HEX", into=c("HEX.ct", "HEX.tslope", "HEX.rr", "HEX.eb", "HEX.result"), sep="_") %>%
          separate(col="IC", into=c("IC.ct", "IC.tslope", "IC.rr", "IC.eb", "IC.result"), sep="_") %>%
          separate(col="RED647", into=c("RED647.ct", "RED647.tslope", "RED647.rr", "RED647.eb", "RED647.result"), sep="_") %>%
          separate(col="ROX", into=c("ROX.ct", "ROX.tslope", "ROX.rr", "ROX.eb", "ROX.result"), sep="_")
     spreaded3 = spreaded2 %>% ungroup %>% group_by(Run.ID, FusionTestOrder) %>% mutate(replicate=seq_along(FusionTestOrder))
     return(spreaded3)
}
pq.s = long.to.wide(pq)

if(params$assay=="paraflu"){
     temp.table =
          pq.s %>% ungroup() %>%
          filter(pslv) %>%
          mutate(FAM.Result = ifelse(FAM.result == 1, "POS", "NEG"),
                 HEX.Result = ifelse(HEX.result == 1, "POS", "NEG"),
                 IC.Result = ifelse(IC.result == 1, "POS", "NEG"),
                 RED647.Result = ifelse(RED647.result == 1, "POS", "NEG"),
                 ROX.Result = ifelse(ROX.result == 1, "POS", "NEG")) %>%
          select(Sample.Name, Flag, FusionTestOrder, test.order, WellID, replicate,
                 FAM.ct:FAM.eb, FAM.Result, HEX.ct:HEX.eb, HEX.Result,
                 IC.ct:IC.eb, IC.Result, RED647.ct:RED647.eb, RED647.Result,
                 ROX.ct:ROX.eb, ROX.Result, filename, ud.filename)

     hiding.vect = which(colnames(temp.table) %in% c("FAM.ct", "FAM.tslope", "FAM.eb",
                                       "HEX.ct", "HEX.tslope", "HEX.eb",
                                       "IC.ct", "IC.tslope", "IC.eb",
                                       "RED647.ct", "RED647.tslope", "RED647.eb",
                                       "ROX.ct", "ROX.tslope", "ROX.eb",
                                       "filename", "replicate", "ud.filename"))
     datatable(
       temp.table,
       extensions = c('Buttons'),
       options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', I('colvis')), pageLength = 10,
                      columnDefs = list(list(targets = hiding.vect,
                                             visible = FALSE)))
       )
} else{
     cat("Not supported for other assays")
}
```

# Negative Samples
Raw RFU.Range data of Panel A and Negative Control (if present):
``` {R, result='asis', echo=FALSE, cache=FALSE}
if(params$assay == "paraflu"){
     temp.table.2 = pq.s %>% ungroup() %>%
          filter(nslv) %>%
          mutate(FAM.Result = ifelse(FAM.result == 1, "NEG", "POS"),
                 HEX.Result = ifelse(HEX.result == 1, "NEG", "POS"),
                 IC.Result = ifelse(IC.result == 1, "POS", "NEG"),
                 RED647.Result = ifelse(RED647.result == 1, "NEG", "POS"),
                 ROX.Result = ifelse(ROX.result == 1, "NEG", "POS")) %>%
          select(Sample.Name, Flag, FusionTestOrder, test.order, WellID, replicate,
                 FAM.ct:FAM.eb, FAM.Result, HEX.ct:HEX.eb, HEX.Result,
                 IC.ct:IC.eb, IC.Result, RED647.ct:RED647.eb, RED647.Result,
                 ROX.ct:ROX.eb, ROX.Result, filename, ud.filename)

     datatable(
       temp.table.2, 
       extensions = c('Buttons'),
       options = list(dom = 'Bfrtip', buttons = c('copy', 'csv', I('colvis')), pageLength = 10,
                      columnDefs = list(list(targets = hiding.vect,
                                             visible = FALSE)))
       )
} else{
     cat("Functionality not supported.")
}
```

#Summary Plots

```{R, result='asis', echo=FALSE, cache=FALSE}
#Chunk for computation
                    # graphing="FVF"
                    # graphing="time"


if(params$graphing == "FVF"){
     
     print("Corresponding Xgroup to filename:")
     print(levels(as.factor(pq$filename)))
     
     pq$filename = as.numeric(as.factor(pq$filename))

     p1 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="RFU.Range", color.by="sample.type", ygroups="Channel", xgroups="filename")
     
     pq$ct[is.na(pq$ct)] = 45
     p2 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="ct", color.by="sample.type", ygroups="Channel", xgroups="filename", 
                     accept.neg=data.frame(Channel=c("FAM", "HEX", "ROX", "RED647", "IC"), AcceptVal=c(35,35,35,35,35)),
                     accept.pos=data.frame(Channel=c("FAM", "HEX", "ROX", "RED647", "IC"), AcceptVal=c(35,35,35,35,35)))
     
     p3 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="EstimatedBaseline", color.by="sample.type", ygroups="Channel", xgroups="filename")
} else if(params$graphing == "time"){
     pq$completion.date = as.Date(pq$completion.date)
     
     p1 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="RFU.Range", color.by="sample.type", ygroups="Channel", xgroups="completion.date")
     
     pq$ct[is.na(pq$ct)] = 45
     p2 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="ct", color.by="sample.type", ygroups="Channel", xgroups="completion.date", 
                     accept.neg=data.frame(Channel=c("FAM", "HEX", "ROX", "RED647", "IC"), AcceptVal=c(35,35,35,35,35)),
                     accept.pos=data.frame(Channel=c("FAM", "HEX", "ROX", "RED647", "IC"), AcceptVal=c(35,35,35,35,35)))
     
     p3 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="EstimatedBaseline", color.by="sample.type", ygroups="Channel", xgroups="completion.date")
} else if(params$graphing == "instrument"){
     p1 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="RFU.Range", color.by="sample.type", ygroups="Channel", xgroups="pantherSN")
     
     pq$ct[is.na(pq$ct)] = 45
     p2 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="ct", color.by="sample.type", ygroups="Channel", xgroups="pantherSN", 
                     accept.neg=data.frame(Channel=c("FAM", "HEX", "ROX", "RED647", "IC"), AcceptVal=c(35,35,35,35,35)),
                     accept.pos=data.frame(Channel=c("FAM", "HEX", "ROX", "RED647", "IC"), AcceptVal=c(35,35,35,35,35)))
     
     p3 = summary.pq.plot(dat=pq, xvar="sample.type", yvar="EstimatedBaseline", color.by="sample.type", ygroups="Channel", xgroups="pantherSN")
} else{
     print("Not a valid option.")
}
```

##RFU Range
```{R, fig.width=12, fig.height=6, echo=FALSE, cache=FALSE}
print(p1)
```

##Ct Non-Normalized
```{R, fig.width=12, fig.height=6, echo=FALSE, cache=FALSE}
print(p2)
```

##Estimated Baseline
```{R, fig.width=12, fig.height=6, echo=FALSE, cache=FALSE}
print(p3)
```